Hydras \& Co.

### 2022-04-13 doc/gaia-chapter.tex
fix a typo

 Paths with constant index and paths whose index is incremented by 1 at each step play an important role in the so-called Ketonen-Solovay machinery~\cite{KP81}.

>>>>

 Paths with constant index and paths whose index is incremented by 1 at each step play an important role in the so-called Ketonen-Solovay machinery~\cite{KS81}.
